Alexis Roche

### 2021-09-02 cv/cv.tex
Add CV in PDF format
Update CV

\ \\
\head{Engineer Degree (equivalent MSc) (1993--1996)}{Ecole Centrale Paris (now CentraleSupelec), France}
\nopagebreak
\begin{itemize}
\item Third year specialization in Applied Mathematics.
\end{itemize}

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Computer skills:}
\ \\ 
\ \\
\ \\ 
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Programming languages: C, Python, Matlab, R. \\
{\tiny$\bullet$} Python packages: numpy, scipy, pylab, skimage, opencv, sklearn, pytorch, tensorflow, keras.\\
{\tiny$\bullet$} C/Python integration via cython.\\
{\tiny$\bullet$} Version control software: git, svn, perforce. \\
{\tiny$\bullet$} Reporting: \LaTeX, MS~Office, OpenOffice, LibreOffice, Google~Docs. \\
\end{minipage}

>>>>

\ \\
\head{Engineer Degree (equivalent MSc) (1993--1996)}{Ecole Centrale Paris (now CentraleSupelec, University Paris-Saclay), France}
\nopagebreak
\begin{itemize}
\item Third year specialization in Applied Mathematics.
\end{itemize}

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{IT skills:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Programming languages: Python, C, C++, Matlab, R. \\
{\tiny$\bullet$} Long-term experience with scientific Python pacakges (numpy, scipy, pylab).\\
{\tiny$\bullet$} CV/AI Python packages: skimage, PIL, opencv, sklearn, pytorch, tensorflow, keras.\\
{\tiny$\bullet$} C/Python integration via Cython.\\
{\tiny$\bullet$} Version control software: git, svn, perforce. \\
{\tiny$\bullet$} Agile workflow (mainly Scrum) using JIRA \& Confluence. \\
{\tiny$\bullet$} Reporting: \LaTeX, MS~Office, OpenOffice, LibreOffice, Google~Docs. \\
\end{minipage}
